Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-02-27 docs/Truman/LocalConservation/paper.tex

\subsection{Double Glazing Problem}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 6 refinements}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
\caption{With graph norm}
\label{fig:doubleglazingGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
\caption{With robust norm}
\label{fig:doubleglazingRobustFlux}
\end{subfigure}
\caption{Flux imbalance in double glazing solutions}
\end{figure}

>>>>

\subsection{Double Glazing Problem}
This nominal problem definition takes the same unit square domain with 
\[
\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad f=0\,;\quad
\hat u=
\begin{cases}
1 & \mbox{on }\Gamma_{right}\\
0 & \mbox{else }
\end{cases}\,,
\]
except that this definition for the boundary is not legal for $\hat u\in
H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The following
results are for $\epsilon=10^{-2}$. Note that $\bbeta=(0,0)^T$ at the center
of the domain.

The choice of test norm appears to have a small effect on the choice mesh
refinement choices as shown in Figure~\ref{fig:doubleglazing}. Other than
that, the conservative and nonconservative solutions behave almost exactly to
the eye. The flux imbalances in Figure~\ref{fig:doubleglazing_flux} are what
we would expect. The nonconservative formulation appears to become more
conservative with refinement.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 6 refinements}
\label{fig:doubleglazing}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
\caption{With graph norm}
\label{fig:doubleglazingGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
\caption{With robust norm}
\label{fig:doubleglazingRobustFlux}
\end{subfigure}
\caption{Flux imbalance in double glazing solutions}
\label{fig:doubleglazing_flux}
\end{figure}

\subsection{Vortex Problem}
This problem models a mildly diffusive vortex convecting fluid in a circle. We
deal with domain $\Omega=[-1,1]^2$ with $\epsilon=10^{-4}$, $\bbeta=(-y,x)^T$,
and $f=0$. Note that $\bbeta=0$ at the domain center. We have an inflow
boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set $\hat
t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
of boundary edges to 1 at corners. We don't enforce an outflow boundary.

Each of the four methods seems to have it's own specific refinement pattern,
but in general we can see that the nonconservative formulations seem to place
much more refinements in the center of the vortex where the solution is
constant. The conservative formulations seem to recognize that more error is
concentrated on the edges of the vortex where we have a sharp change from
constant values to linear growth in terms of radius. Again we see that
standard DPG appears to approach conservation with refinement, and
unfortunately the conservative formulation appears to be losing enforcement
under the robust norm.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graph6nc.png}
\caption{Nonconservative with graph norm}
\label{fig:vortexGraph6nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robust6nc.png}
\caption{Nonconservative with robust norm}
\label{fig:vortexRobust6nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:vortexGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:vortexRobust6c}
\end{subfigure}
\caption{Vortex problem after 6 refinements}
\label{fig:vortex}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graphFlux.pdf}
\caption{With graph norm}
\label{fig:vortexGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robustFlux.pdf}
\caption{With robust norm}
\label{fig:vortexRobustFlux}
\end{subfigure}
\caption{Flux imbalance in vortex solutions}
\label{fig:vortex_flux}
\end{figure}

\subsection{Wedge Problem}
We devised this problem to examine some of the issues we were having blow up
of the solution under the robust test norm. The domain is a rectangle
$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
of the wedge.

When the colorscale is scaled from 0 to 1, the macro view of all of the
solutions looks nearly identical as seen in Figure~\ref{fig:wedge}. However,
we start to see some differences in the refinement patterns in
Figure~\ref{fig:wedge_mesh} indicating that the various methods distribute
error in different ways. We see more evidence of this when we zoom in on the
tip of the wedge where we get a change in boundary conditions. The graph norm
solutions don't exhibit any significant problems here. The nonconservative and
conservative solutions vary smoothly in the range $(-0.00127, 1.03)$, plus or
minus some less significant digits. The nonconservative robust solution jumps
from -19.6 to 20.3 at the tip, though this appears to be a very localized
phenominon. Adding local conservation appears to exacerbate this situation as
the solution varies from -20.0 to 23.2 and appears to polute a larger area of
the problem. We implemented a crude hp-adaptive refinement strategy in order
to try to resolve any singularities present in the solution. If the cell
measure dips below $5\times10^{-4}$, we switch from h-adaptivity to
p-adaptivity. Figure~\ref{fig:wedge_poly} shows the resultant polynomial
orders after refinement. It really appears that the apparent singularities in
the robust solutions are not physical phenomena that just need resolution, but
a weakness in the method with the robust test norm.

We plot the flux imbalances in Figure~\ref{fig:wedge_flux}. Despite the
extreme overshoots and undershoots in the conservative method with the robust
test norm, we still appear to maintain acceptable levels of conservation.

\begin{figure}
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c}
\end{subfigure}
\caption{Wedge problem after 16 refinements}
\label{fig:wedge}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c_mesh}
\end{subfigure}
\caption{Wedge problem mesh after 16 refinements}
\label{fig:wedge_mesh}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_zoom.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_zoom.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c_zoom.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c_zoom.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c_zoom}
\end{subfigure}
\caption{Wedge problem zoomed in after 16 refinements}
\label{fig:wedge_zoom}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_poly.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc_poly}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_poly.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc_poly}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c_poly.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c_poly}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c_poly.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c_poly}
\end{subfigure}
\caption{Wedge problem poly after 16 refinements}
\label{fig:wedge_poly}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graphFlux.pdf}
\caption{With graph norm}
\label{fig:wedgeGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robustFlux.pdf}
\caption{With robust norm}
\label{fig:wedgeRobustFlux}
\end{subfigure}
\caption{Flux imbalance in wedge solutions}
\label{fig:wedge_flux}
\end{figure}
